---
title: "Introduction of SwissAnalysis APP"
author: "ZixinZhang"
date: "26/10/2020"
output: ioslides_presentation
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    message = FALSE)
```

## Introduction

This is a short presentation of APP **swissAnalysis**. This APP provides simple analysis of the dataset ***swiss***, which contains the information of standardized fertility measure and socio-economic indicators for each of 47 French-speaking provinces of Switzerland at about 1888.  

The APP could be accessed from https://zz7sp.shinyapps.io/swissanalysis  
  
The original code of **the APP and this presentation** could be access from https://github.com/7cats/DataProductW4

```{r echo = F}
library(plotly)
data(swiss)
library(ggplot2)
```
## Functions of the APP 

This APP has three basic functions:  

1. Plotting the relation between two variables, which are chosen by users.  

2. Generating fitted regression model for the **whole data set**, or a **subset of the dataset** which the users should select from the plot.  

3. Giving the **$R^2$** of fitted regression models.  

## Input and the reactive output
- If the **box** of ***Fit a regression model*** is ticked, the APP will generate a linear regression model and plot the fitted line. 
  
- If **a subset of the data are selected from the plot**, the APP will generate another linear regression model using this subset of data.
  
- The **$R^2$** of fitted model will be presented below the plot, when box is ticked and area is selected from the plot.


## Example of Fertility and Agriculture:
If **Fertility** and **Agriculture** are chosen are variables to be analyzed (which is the default setting), and a small area are selected, the APP will present this result.  
  
```{r }
DF <- data.frame(Fertility = swiss$Fertility, Agriculture = swiss$Agriculture)
p <- ggplot(DF, aes(Fertility, Agriculture)) +
            geom_point( size = 3) +
            labs( x = colnames(DF)[1], y = colnames(DF)[2], 
                  title = paste("Relation between", colnames(DF)[1],
                                'and', colnames(DF)[2], sep = ' ')) + 
            theme( plot.title = element_text(hjust = 0.5,
                                             face = "bold",
                                             size = 20),
                   axis.title = element_text(size = 15),
                   axis.text = element_text(size = 14))

fitLine <- lm(data = DF, Agriculture ~ Fertility)
pred <- data.frame(Fertility = DF$Fertility, Agriculture = predict(fitLine, DF))
p <- p + geom_line(data = pred, aes(Fertility, Agriculture),
                   color = 'orange', lwd = 1.5)

DFSelect <- DF[which((DF$Fertility >= 64) & (DF$Fertility <= 72) & 
                     (DF$Agriculture <= 75) & (DF$Agriculture >= 46)),]
fitLineSelect <- lm(data = DFSelect, Agriculture ~ Fertility)
predSelect <- data.frame(Fertility = DF$Fertility, Agriculture = predict(fitLineSelect, DF))

p <- p + geom_point(data = DFSelect, aes(Fertility, Agriculture),
                    size = 5, shape = 8) + 
         geom_line(data = predSelect, aes(Fertility, Agriculture),
                   color = 'lightblue', lwd = 1.5)
p
```
